\section{Conclusion}
\label{sec:conclusion}

This laboratory assignment had as the main objective the construction and analysis of an audio amplifier. The chosen design is present in figure \ref{circuit}. The goal was to maximise the voltage gain and the bandwidth at which the circuit operates at ``full capacity'', while minimising the cost and the lower cutoff frequency, preferably to less than $20\;Hz$, the lower limit of the audible range.

We designed two circuits, as explained in \ref{sec:simulation}, with two objectives in mind. By analysing the results obtained, we conclude that we were able to achieve a good result in either of the circuits designed, with high gain and low cost. Unfortunately we were not able to lessen the lower cutoff limit any more without lessening the merit. We also tried to lessen the output impedance, but this was not possible for the same reason.

The merit figure of our first circuit is: \input{../sim/merit}. For our second circuit, it's \input{../sim/merit_mb}.


\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
        $V$ & $V_t$ & $V_s$ & $|V_t-V_s|$ & $Error (\%)$ \\
        \hline
        \hline
        \input{comparison}
        \hline
  \end{tabular}
  \caption{Theoretical values ($V_t$) and Simulation values ($V_s$) of the operating point analysis (table produced with {\bf Python})  - The absolute deviation and error presented here are rounded up to one significant digit, for ease of interpretation.}
  \label{error1_res}
\end{table}


Some deviations between the simulation and theoretical results were expected, due to the different model used by {\bf Ngspice} for transistors. In the theoretical analysis, we used very simple models. These deviations can be observed not only in table \ref{error1_res}, but also by comparing figures \ref{vg} and \ref{fig:frequencyresp} and the gains and impedances computed.

All in all, the objectives were met. With more time and a lengthier study, better results could be obtained, and other solutions implemented.
